### 2014-09-18 ApTranscriptome_TR.Rmd
Completed analysis of replicated Sailfish gene expression quantification. Turns out that quantification is *very* consistent among repeated runs. The differences between my previous and current results are (probably) due to upgraded version of the Sailfish software.

# loop across replicates
reps <- c("rep1", "rep2", "rep3", "rep4", "rep5", "rep6", "rep7", "rep8", "rep9", "rep10")

for(sr in reps) {
  read.sailfish.reps(sr, fd=sfexpressionroot, repout=paste("TPM.dt.", sr, sep=""))
  }
```

@@

# setkey of each TPM replicate to 'Transcript'
ls1 <- ls(pattern="TPM")
sapply(mget(ls1), function(x) setkey(x, Transcript))
# remove Transcripts found in contaminant list
sapply(mget(ls1), function(x) x[!cont.list])

# remove from annotation.table
setkey(annotation.table, Sequence.Name)
annotation.table <- annotation.table[!cont.list]
str(annotation.table)
```

@@

# calculate overall P value and R^2 for each transcript
RxNpval <- ddply(TPM.dt.sub, .(Transcript), .inform="TRUE", modpFunc)
```

@@

```{r padjust}
RxNpval$padj <- p.adjust(RxNpval$pval, method = "fdr")
# Plot FDR values against initial pvalues
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)

# subset to significant transcripts
signif.transcripts <- RxNpval[which(RxNpval$padj < 0.05), ]

>>>>

# replicates
reps <- c("rep1", "rep2", "rep3", "rep4", "rep5", "rep6", "rep7", "rep8", "rep9", "rep10")

# loop across replicates and load expression data
for(sr in reps) {
  read.sailfish.reps(sr, fd=sfexpressionroot, repout=paste("TPM.dt.", sr, sep=""))
}
```

@@

# setkey of each TPM replicate to 'Transcript'
ls1 <- ls(pattern="TPM.dt.rep")
sapply(mget(ls1), function(x) setkey(x, Transcript))
sapply(mget(ls1), function(x) key(x))
# remove Transcripts found in contaminant list
TPM.dt.rep1 <- TPM.dt.rep1[!cont.list]
TPM.dt.rep2 <- TPM.dt.rep2[!cont.list]
TPM.dt.rep3 <- TPM.dt.rep3[!cont.list]
TPM.dt.rep4 <- TPM.dt.rep4[!cont.list]
TPM.dt.rep5 <- TPM.dt.rep5[!cont.list]
TPM.dt.rep6 <- TPM.dt.rep6[!cont.list]
TPM.dt.rep7 <- TPM.dt.rep7[!cont.list]
TPM.dt.rep8 <- TPM.dt.rep8[!cont.list]
TPM.dt.rep9 <- TPM.dt.rep9[!cont.list]
TPM.dt.rep10 <- TPM.dt.rep10[!cont.list]

# remove contaminants from annotation.table
setkey(annotation.table, Sequence.Name)
annotation.table <- annotation.table[!cont.list]
str(annotation.table)
```

@@

# calculate overall P value and R^2 for each transcript
RxNpval.r1 <- ddply(TPM.dt.rep1, .(Transcript), .inform="TRUE", modpFunc)
RxNpval.r2 <- ddply(TPM.dt.rep2, .(Transcript), .inform="TRUE", modpFunc)
RxNpval.r3 <- ddply(TPM.dt.rep3, .(Transcript), .inform="TRUE", modpFunc)
RxNpval.r4 <- ddply(TPM.dt.rep4, .(Transcript), .inform="TRUE", modpFunc)

@@

```{r padjust}
RxNpval.r1$padj <- p.adjust(RxNpval.r1$pval, method = "fdr")
RxNpval.r2$padj <- p.adjust(RxNpval.r2$pval, method = "fdr")
RxNpval.r3$padj <- p.adjust(RxNpval.r3$pval, method = "fdr")
RxNpval.r4$padj <- p.adjust(RxNpval.r4$pval, method = "fdr")

# Plot FDR values against initial pvalues
par(mfrow = c(2,1))
hist(RxNpval$pval)
hist(RxNpval$padj)

# subset to significant transcripts
signif.transcripts.r1 <- RxNpval.r1[which(RxNpval.r1$padj < 0.05), ]
signif.transcripts.r2 <- RxNpval.r2[which(RxNpval.r2$padj < 0.05), ]
signif.transcripts.r3 <- RxNpval.r3[which(RxNpval.r3$padj < 0.05), ]
signif.transcripts.r4 <- RxNpval.r4[which(RxNpval.r4$padj < 0.05), ]
